\documentclass[10pt, dvipsnames, table, aspectratio=169]{beamer}

\usetheme[progressbar=frametitle]{metropolis}

\usepackage{appendixnumberbeamer}

\usepackage{booktabs}

\usepackage[scale=2]{ccicons}

\usepackage{pgfplots}

\usepgfplotslibrary{dateplot}

%Project imports:

\usepackage[color=yellow]{todonotes}

\usepackage{hyperref}

\urlstyle{same}  % don't use monospace font for urls

%Project code:

\hypersetup{unicode=true,pdftitle={},pdfauthor={},
pdfkeywords={},pdfborder={0 0 0},breaklinks=true}

\makeatletter

%Document:

\title{Software Sustainability Workshop}

\subtitle{}

\date{December 9th}

\author{Martin Chapman}

\institute{King's College London}

\begin{document}

%\maketitle

%==============================

\begin{frame}[fragile]{Workshops in the time of COVID}

The online material, which you have already reviewed, is the
`\textbf{lecture}'.

\begin{itemize}

    \item Available on \textbf{YouTube}.

    \item Catch up as quickly as you can if you have not yet reviewed
    this material.

\end{itemize}

Today is the `\textbf{tutorial}'.

\begin{itemize}

    \item Complete a set of \textbf{exercises} based on the course
    material.

\end{itemize}

Links to all material available at:
\href{https://github.com/martinteaching/sustainability2020}{github.com/martinteaching/sustainability2020}.

\end{frame}

%==============================

\begin{frame}[fragile]{Forums}

Exercise rooms, on \textbf{Teams}:

\begin{enumerate}

    \item To be joined during the exercise sections of the workshop
    (live stream pauses). Ask for help from me, and from your peers.

\end{enumerate}

\textbf{Slack}:

\begin{enumerate}

    \item For asking questions in text throughout, and if everything
    goes wrong.

\end{enumerate}

\textbf{YouTube live}, where we are now:

\begin{enumerate}

    \item The day will be coordinated from here, and will be where the
    solution to each stage of the exercise is shown.

    \item Questions asked in the first two fora will inform what's
    discussed here (be aware of stream delays).

\end{enumerate}

\end{frame}

%==============================

\begin{frame}[fragile]{Structure}

\centering

\begin{table}[h!]

    \centering

    \scalebox{0.75}{\input{tables/workshop-schedule}}

\end{table}

\end{frame}

%==============================

\begin{frame}[fragile]{Assessment}

A requirement for the workshop.

\textbf{Highlighted in the exercises}, including submission and marking
process.

Please complete by the \textbf{end of the week}, to receive a mark.

\end{frame}

%==============================

\begin{frame}[fragile]{A quick word on how I like to run sessions...}

I never consider myself an expert. Always an \textbf{enthusiast}.

Likely people here who know \textbf{way more} about aspects of this
technology than I do.

Correct me, challenge me and tell me better ways to do things - I am
here to \textbf{learn too}.

Most importantly, collaborate and help \textbf{each other}.

\end{frame}

%==============================

\begin{frame}[fragile]{KCLHI and software sustainability: microservices}

King's College London Health Informatics (KCLHI).

\begin{itemize}

    \item \href{https://kclhi.org}{kclhi.org}.
    
    \item \href{https://github.com/kclhi}{github.com/kclhi}.
    
\end{itemize}

Microservice architectures:

\begin{itemize}
    
    \item `\textbf{Phenoflow}' - \href{https://github.com/kclhi/phenoflow}{github.com/kclhi/phenoflow}.
    
    \item `\textbf{CONSULT}' - \href{https://github.com/kclconsult}{github.com/kclconsult}.
    \item `\textbf{TMRWeb}' - \href{https://github.com/kclconsult/tmrweb}{github.com/kclconsult/tmrweb}.
    
\end{itemize}

\end{frame}

\end{document}
