\documentclass[10pt, dvipsnames, table, aspectratio=169]{beamer}

\usetheme[progressbar=frametitle]{metropolis}

\usepackage{appendixnumberbeamer}

\usepackage{booktabs}

\usepackage[scale=2]{ccicons}

\usepackage{pgfplots}

\usepgfplotslibrary{dateplot}

%Project imports:

\usepackage[color=yellow]{todonotes}

\usepackage{hyperref}

\urlstyle{same}  % don't use monospace font for urls

%Project code:

\hypersetup{unicode=true,pdftitle={},pdfauthor={},pdfkeywords={},pdfborder={0 0 0},breaklinks=true}

\makeatletter

%Document:

\title{Software Sustainability Workshop}

\subtitle{}

\date{February 2nd}

\author{Martin Chapman}

\institute{King's College London}

\begin{document}

%\maketitle

%==============================

\begin{frame}[fragile]{Teaching format}

The online material, which you have already reviewed, is the `\textbf{lecture}'.

\begin{itemize}

    \item Available on \textbf{YouTube} (recorded offline and via live stream).

    \item Catch up as quickly as you can if you have not yet reviewed this material.

\end{itemize}

Today is the `\textbf{tutorial}'.

\begin{itemize}

    \item A \textbf{workshop} in which we further explore the ideas from the course.

\end{itemize}

Links to all material available at:
\href{https://github.com/martinteaching/sustainability}{\textbf{github.com/martinteaching/sustainability}}.

\end{frame}

%==============================

\begin{frame}[fragile, allowframebreaks]{Structure}

A series of \textbf{Teams} sessions, each centred around one of the five course topics:

\begin{centering}

\begin{table}[h!]

    \centering

    \input{tables/workshop-schedule}

\end{table}

\end{centering}

\framebreak

There is an \textbf{exercise} available for each session, based on the current topic.

The first part of each session will give you time \textbf{individually} to review and make a start on the exercise.

The second will be a \textbf{collaborative} coding session, during which we will construct an answer to the exercise together.

\begin{itemize}

  \item I will share a \emph{JupyterLab} link via Teams.

  \item We will take it in turns to be \textbf{in charge of the editor}, with those not currently coding \textbf{helping with the solution}.

\end{itemize}

\end{frame}

%==============================

\begin{frame}[fragile]{Assessment}

A requirement for the workshop.

Please \textbf{engage sufficiently with the interactive coding sessions} in order to receive a `pass' mark.

\end{frame}

%==============================

\begin{frame}[fragile]{A quick word on how I like to run sessions...}

I never consider myself an expert. Always an \textbf{enthusiast}.

Likely people here who know \textbf{way more} about aspects of this technology than I do.

Correct me, challenge me and tell me better ways to do things -- I am here to \textbf{learn too}.

Most importantly, collaborate and help \textbf{each other}.

\end{frame}

%==============================

\begin{frame}[fragile]{KCLHI and software sustainability: microservices}

A \textbf{microservice architecture} is really what we are building towards in this course, as they epitomise sustainable software.

An approach we use in our group, King's College London Health Informatics (KCLHI).

\begin{itemize}

    \item \href{https://kclhi.org}{kclhi.org}.
    
    \item \href{https://github.com/kclhi}{github.com/kclhi}.
    
\end{itemize}

Examples:

\begin{itemize}
    
    \item `\textbf{Phenoflow}' - \href{https://github.com/kclhi/phenoflow}{github.com/kclhi/phenoflow}.    
    \item `\textbf{CONSULT}' - \href{https://github.com/kclconsult}{github.com/kclconsult}.
    \item `\textbf{TMRWeb}' - \href{https://github.com/kclconsult/tmrweb}{github.com/kclconsult/tmrweb}.
    \item `\textbf{REFLECT}' - \href{https://github.com/kclreflect}{github.com/kclreflect}.
    
\end{itemize}

\end{frame}

\end{document}
